Global Reach or Out of Reach

### 2019-05-10 Paper_markdown.Rmd
Still working

---
title: "Global Reach or Out of Reach"
author: "Addison Huygens"
date: "May 10, 2019"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: no
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
  word_document: default
citecolor: black
biblio-style: apsr
endnote: no
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("tidyverse")
install.packages("DataCombine")
install.packages("dotwhisker")
install.packages("data.table")
install.packages("mlogit")
install.packages("margins")
install.packages("nnet")
install.packages("reshape2")

library(plyr)
library(tidyverse)
library(DataCombine)
library(haven)
library(dotwhisker)
library(data.table)
library(mlogit)
library(ggplot2)
library(margins)
library(nnet)
library(reshape2)

@@

```
#Data generation process 
#Prepping datasets for merging.

@@

Master <- politically_relevant %>%
  rename(
    ccodea = ccode1,
    ccodeb = ccode2, 
  ) 
view(Master)
```

```
#Merging datasets

#mergin in dyadic mid data
Master2 <- full_join(Master, Dyadic_MID, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
summary(Master2)

Master2 <- merge(Master, Dyadic_MID, by=c("ccodea", "ccodeb", "year"), all.x = TRUE, all.y = TRUE)

Master2 <- left_join(Master2, Alliance, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))

#Merging in polity iv datasets a and b.
Master2 <- left_join(Master2, PolityIVa, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
Master2 <- left_join(Master2, PolityIVb, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
summary(Master2)

#merging in data on US naval capabilities
Master2 <- left_join(Master2, USNaval, by=c("year"), copy=FALSE, suffix=c("x", "y"))

@@

#merging in data on material capabilities
Master2 <- left_join(Master2, NMCA, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
Master2 <- left_join(Master2, NMCB, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))

@@

```
#Variable Generation

@@

#Creating a variable which only identifies if a Mid which involved the use of force occured in that dyad-year.
Master3 <- Master3 %>%
    mutate(Use_Force = ifelse(hihost > 3, 1, 0))
Master3$Use_Force[is.na(Master3$Use_Force)] <- 0
summary(Use_Force)
ftable(Use_Force)

@@

#Variable identfying the presence of an alliance between the two members of the dyad
Master3 <- Master3 %>%
    mutate(Ally = ifelse(atopally == "1", 1, 0))
    mutate(Ally[is.na(Ally)] <- 0))
    summary(Master3$atopally)
summary(Master3$Ally)
head(Master3$Ally, 1000)

@@

plot(Master5$year, Master5$US_Naval_Cap, main="US Naval Capabilities Over Time",
    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master5$year,Master5$US_Naval_Cap), col="blue"))

@@

Master4 <- Master3 %>%
    mutate(Ally =0)
Master4$Ally[Master4$neutrality==1] <- 1 
Master4$Ally[Master4$nonaggression==1] <- 1 
Master4$Ally[Master4$defense==1] <- 1 
Master4$Ally[Master4$entente==1] <- 1

Master4 <- select(Master4, ccodea, ccodeb, year, Mid, Use_Force, Hostility, US_Naval_Cap, Same_Region, Contiguous, Joint_Dem, Relative_Cap, Major, Post_Cold_War, Lag_Mid, Ally)
summary(Master4)
```

```
#Statistical Tests

@@

#Full Models
  #Logistic regression
MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Ally, data = Master4, family=binomial)
summary(MID_Full_Log) 
dwplot(MID_Full_Log)

Master5 <- Master3 %>%
    mutate(Relative_Cap = cinca/cincb)

MID_Full_Log2 <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master5, family=binomial)
summary(MID_Full_Log2)
dwplot(MID_Full_Log2, show_intercept=TRUE, model_name = "Logistic Model", vline=geom_vline(xintercept=0), dot_args = list(size=3))
exp(coef(MID_Full_Log2))

margins(MID_Full_Log2)
margins(MID_Full_Log2, at = list(US_Naval_Cap = 0:1))
cplot(MID_Full_Log2, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of MID given US naval capabilities")

Force_Full_Log2 <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master5, family=binomial)
summary(Force_Full_Log2)
dwplot(Force_Full_Log2, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))
exp(coef(Force_Full_Log2))
test1 <- data.frame(exp(coef(Force_Full_Log2)))
ggplot(exp(coef(Force_Full_Log2)))

>>>>

---
title: "Global Reach or Out of Reach"
author: "Addison Huygens"
date: "May 10, 2019"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: no
    latex_engine: pdflatex
    template: svm-latex-ms2.tex.url
  word_document: default
citecolor: black
biblio-style: apsr
endnote: no
fontsize: 12pt
---

options(tinytex.verbose = TRUE)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(plyr)
library(tidyverse)
library(DataCombine)
library(haven)
library(dotwhisker)
library(data.table)
library(mlogit)
library(ggplot2)
library(margins)
library(nnet)
library(reshape2)

@@

```{r, include=FALSE, cache=TRUE}
options(tinytex.verbose = TRUE)
#Data generation process 
#Prepping datasets for merging.

@@

Master <- politically_relevant %>%
  rename(
    ccodea = ccode1,
    ccodeb = ccode2, 
  ) 
view(Master)

```{r, include=FALSE, cache=TRUE}
options(tinytex.verbose = TRUE)
#Merging datasets

#mergin in dyadic mid data
Master2 <- merge(Master, Dyadic_MID, by=c("ccodea", "ccodeb", "year"), all.x = TRUE, all.y = TRUE)

Master2 <- merge(Master2, Alliance, by=c("ccodea", "ccodeb", "year"), all.x = TRUE)

#Merging in polity iv datasets a and b.

Master2 <- merge(Master2, PolityIVa, by=c("ccodea", "year"), all.x = TRUE)

Master2 <- merge(Master2, PolityIVb, by=c("ccodeb", "year"), all.x = TRUE)

#merging in data on US naval capabilities

Master2 <- merge(Master2, USNaval, by=c("year"), all.x = TRUE)

@@

#merging in data on material capabilities
Master2 <- merge(Master2, NMCA, by=c("ccodea", "year"), all.x = TRUE)

Master2 <- merge(Master2, NMCB, by=c("ccodeb", "year"), all.x = TRUE)

@@

```{r, include=FALSE, cache=TRUE}
options(tinytex.verbose = TRUE)
#Variable Generation

@@

#Creating a variable which only identifies if a Mid which involved the use of force occured in that dyad-year.
Master3 <- Master3 %>%
    mutate(Use_Force = ifelse(hihost > 3, 1, 0))
Master3$Use_Force[is.na(Master3$Use_Force)] <- 0
summary(Master3$Use_Force)
ftable(Master3$Use_Force)

@@

#Variable identfying the presence of an alliance between the two members of the dyad
Master3 <- Master3 %>%
    mutate(Ally =0)
Master3$Ally[Master3$neutrality==1] <- 1 
Master3$Ally[Master3$nonaggression==1] <- 1 
Master3$Ally[Master3$defense==1] <- 1 
Master3$Ally[Master3$entente==1] <- 1

@@

plot(Master3$year, Master3$US_Naval_Cap, main="US Naval Capabilities Over Time",
    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master3$year,Master3$US_Naval_Cap), col="blue"))

@@

Master4 <- select(Master3, ccodea, ccodeb, year, Mid, Use_Force, Hostility, US_Naval_Cap, Same_Region, Contiguous, Joint_Dem, Relative_Cap, Major, Post_Cold_War, Lag_Mid, Ally)
summary(Master4)
```

```{r, include=FALSE, cache=TRUE}
options(tinytex.verbose = TRUE)
#Statistical Tests

@@

#Full Models
  #Logistic regression
MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Ally, data = Master4, family=binomial)
summary(MID_Full_Log)

dwplot(MID_Full_Log, show_intercept=TRUE, model_name = "Logistic Model", vline=geom_vline(xintercept=0), dot_args = list(size=3))
exp(coef(MID_Full_Log))

margins(MID_Full_Log)
margins(MID_Full_Log, at = list(US_Naval_Cap = 0:1))
cplot(MID_Full_Log2, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of MID given US naval capabilities")

Force_Full_Log2 <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master4, family=binomial)
summary(Force_Full_Log2)
dwplot(Force_Full_Log2, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))
exp(coef(Force_Full_Log2))
test1 <- data.frame(exp(coef(Force_Full_Log2)))
ggplot(exp(coef(Force_Full_Log2)))
